Adolescent well-being in the digital age

### 2022-01-28 00-clean.qmd
Update GBD data with older ages

# Confirm that correct measures were downloaded:
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

@@

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))

# Focus on young people
gbd <- gbd %>%
  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
```

>>>>

# Confirm that correct measures were downloaded:
distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

@@

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))
```
